Bayesian Restricted Likelihood Methods: Conditioning on Insufficient Statistics in Bayesian Regression\thanksref{T1}

### 2019-06-04 revision_2/response/response.tex

\documentclass{article}
\usepackage{amsthm}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue,filecolor=blue,backref=page]{hyperref}
\usepackage{graphicx}
\usepackage{graphicx, psfrag, amsfonts, float}
\usepackage{natbib}
\usepackage{amsthm}
\usepackage{multirow}
\usepackage{hhline}
 \pdfminorversion=4
\usepackage{rotating}
\def\bgam{\mbox{\boldmath $\gamma$}}
\def\bth{\mbox{\boldmath $\theta$}}
\def\bbeta{\mbox{\boldmath $\beta$}}
\def\blam{\mbox{\boldmath $\lambda$}}
\def\bmu{\mbox{\boldmath $\mu$}}

\newcommand{\bx}{\mbox{\boldmath $x$}}
\newcommand{\bu}{\mbox{\boldmath $u$}}
\newcommand{\bc}{\mbox{\boldmath $c$}}
\newcommand{\bs}{\mbox{\boldmath $s$}}
\newcommand{\by}{\mbox{\boldmath $y$}}
\newcommand{\bz}{\mbox{\boldmath $z$}}
\newcommand{\bv}{\mbox{\boldmath $v$}}
\newcommand{\bb}{\mbox{\boldmath $b$}}
\newcommand{\bzero}{\mbox{\boldmath $0$}}
\newcommand{\thstarj}{\mbox{$\theta^\star_j$}}
\newcommand{\bths}{\mbox{$\btheta^\star$}}
\newcommand{\pkg}[1]{{\fontseries{b}\selectfont #1}}

\newcommand{\ud}{\mathrm{d}}
\newcommand{\uI}{\mathrm{I}}
\newcommand{\uP}{\mathrm{P}}
\newcommand{\up}{\mathrm{p}}
\newcommand{\mb}{\mathbf}
\newcommand{\mc}{\mathcal}

\newcommand{\Bern}{\mbox{Bern}}
\newcommand{\Nor}{\mbox{N}}
\newcommand{\Ga}{\mbox{Gamma}}
\newcommand{\Dir}{\mbox{Dir}}
\newcommand{\Ber}{\mbox{Ber}}
\newcommand{\Be}{\mbox{Be}}
\newcommand{\Unif}{\mbox{Unif}}
\newcommand{\Binom}{\mbox{Bin}}
\newcommand{\IG}{\mbox{IG}}

\newcommand{\Xs}{X^\star}
\newcommand{\Lc}{{\cal L}}

\usepackage[dvipsnames,usenames]{color}
\newcommand{\yy}{\color{magenta}\it}
\newcommand{\jj}{\color{Black}\rm}
\newcommand{\yjnote}[1]{\footnote{\color{Brown}\rm #1 \color{Black}}}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{definition}[theorem]{\bf Definition}
\newtheorem{lemma}[theorem]{\bf Lemma}
\newtheorem{corollary}[theorem]{\bf Corollary}
\newtheorem{proposition}[theorem]{\bf Proposition}
\newtheorem{assumption}[theorem]{\bf Assumption}
\newtheorem{example}[theorem]{\bf Example}
\newtheorem{remark}[theorem]{\bf Remark}

\newcommand{\iid}{\stackrel{iid}{\sim}}
\newcommand{\indep}{\stackrel{indep}{\sim}}

\setlength{\textwidth}{6 in}
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}{figs/}}

\begin{document}

\section{Reviewer 1 Comments}

\begin{enumerate}
\item The authors propose a broad class of the proposal density, but didn’t discuss the choice and tuning within the class. Tuning the proposal is crucial to the mixing and efficiency of the MH algorithm, epecially in the high-dimension space, n ? p-dimensional, that the paper is dealing with. There are two difficulties in tuning within the proposed class. First, since the proposal density is a complicated transformation of p(z?) in Rn?p?1, even if p(z?) belongs to a standard parametric family, p(yp|?) does not and it is not straightforward to assess the properties that are usually used in tuning MCMC algorithm, e.g. mode and
tails behaviour. Second, the proposed algorithm (11) is restrictive because it only works for independent proposal, not the random walk proposal. Random walk is more able to explore a non-standard parameter space like the manifold here, while it seems tricky to design the independent proposal that well covers the probability mass of the target density, which again due to the transformation.
\item The simulation studies didn’t report the choice of p(z?), acceptance rates of the MH, and mixing of the overall MCMC algorithm. Due to point 1, I think these issues would be of interest to readers.
\item The models studied in both the simulation and real data examples are just simple linear regression which is not realistic. Multiple linear regression with at least three independent variables should be studied.
\item What are the benefits of the proposed method over the classical robust point estimators, like Huber or Tukey estimators compared in the examples, to offset the additional compu- tational cost and tuning efforts? From the simulation studies, whether it has improvement or not depends on the prior distribution, which seems to be from comparing Bayesian and Frequentist methods. Actually, literatures on the asymptotic properties of f(?|T(yobs)) shows that, if T (yobs) is asymptotically unbiased, T (yobs) and E(? | T (yobs)) have the same asymptotic variance. Hence if the prior doesn’t matter, both methods have similar performance.
\item I think f(?|T(yobs)) might perform better in the following scenario: when T(yobs) is asymp- totically biased, E(?|T(yobs)) can still be asymptotically unbiased as long as the true pa- rameter is identifiable conditioning on the summary statistic, i.e the value of E(T(yobs)) is unique on the true parameter. One possible example is the robust ridge-regression estimator, but it needs further investigation whether this estimator satisfies C1-C8.
\item In page 14, should C?(X) n ? p-dimensional instead of n ? p ? 1-dimensional?
\end{enumerate}

\section{Reviewer 2 Comments}

\begin{enumerate}
\item Is the proposed framework useful for practitioners? The proposed framework targets scenario where (i) we know the data is a mixture of good and bad data, and (ii) we only want to “build models that offer good prediction for the good portion of the data” (from the 1st paragraph of Sec 5). Authors should provide real examples in which (i) and (ii) hold. In any real examples, (i) often holds, but (ii) doesn’t: if we already have had a contaminated training sample, why would we expect the test sample to contain only the good portion? In many real applications, learning the heterogeneity of the good and bad samples is precisely the goal of statistical data analysis.
For the insurance example analyzed in Sec 6, the authors should provide ev- idence, e.g., literature from actural science or white papers from insurance industry, to justify why it makes sense to assume (i) and (ii) hold.
\item As a methodological paper, what’s the guideline/recommendation given by the authors? After reading this paper, I don’t know how to apply the suggested framework
on a simple regression model. Apparently, the choice of the likelihood func-
tion (for the good data) f(·|?) and the choice of the statistic T are related.
To make things more complicated, each has multiple choices. For example, f could be normal, student-t or other heavy-tailed distribution; T could be something named Huber or Tukey although the authors are not even bothered to provide any mathematical expression.

Instead of just reporting numerical performance, the authors should provide some guidelines/recommendation on how to apply their framework on linear regression models, e.g., what are the default choices for f and T ? Is there any- way to select which f or T to use based on cross-validation or other empirical methods?
\item What’s the real benefit of this computationally expensive approximation framework? The proposed framework replies on a good summary statistic T(yobs), which
has already provided a robust estimate of the target parameter. On the other
hand, the proposed MCMC algorithm is computationally expensive. In Sec
4.2, the authors only discussed the computation cost for their proposal dis- tribution, but ignored the computation cost for obtaining T(y) (see Theorem 4.1). Those statistics are M-estimators, i.e., they are maximizers of some objective functions involving n observations and p parameters. The authors should discuss the computation cost for T(y).
What’s the gain of all the extra computation? The authors compare KL diver- gence, but 1) few real applications care about KL divergence not mentioning the predictive density f(y?|M,yobs) is not available in closed-form; 2) since f(y?|M,yobs) is not available close-form, the KL divergence is approximated and it’s not clear to me how accurate the approximation is.
The authors should compare prediction and estimation accuracy, common met- rics used for regression models.
The simulation setup is too simple. Suggest to add some linear regression models with large p and/or large n.
\end{enumerate}

\subsection{Some minor issues.}
\begin{enumerate}
\item  Abstract “... handling data sets with outliers and dealing with model mis- specification. We outline the drawbacks ... and propose a new method as an alternative.” The proposed method cannot handle “model misspecification”, instead it assumes f is the true model (no misspecification) and what’s wrong is part of the data.
\item  Sec 2 and Sec 3 can be shortened or merged.
\item  Eq(2) in Sec 2.1, the notation f(yi|?,c(yi)) is not introduced yet; what’s introduced is f(y|?).

\item  Sec 4.1, C3 and C4: a maximizer may not be a continuous function of the data and it may not be unique. Instead of saying “Many estimators satisfy the above properties”, the authors should list those estimators and explain why those conditions are satisfied.
\item  Bottom of p14, ”Sample z? from a distribution with known density on S.” Any distribution? For example, can it be a point mass or its support has to be equal to S? What’s the sampling distribution for z? used in the simulation studies and real data analysis?
\item  Eq (18): change dy to dy?
\end{enumerate}

\section{AE Comments}
This paper proposes a Bayesian approach for making inference based on robust statistics of the data instead of the original observations. The conditioning robust statistics pass the desirable robustness (to outliers) to the posterior distribution of parameters, thus having the potential to improve inference and prediction. This paper addresses an important problem in statistics and contains interesting ideas. However, there are some major concerns.
The paper focuses on outliers. Although outliers automatically imply that the model is misspecified, model misspecification is much broader including the misspecification of the density of the good data. The paper does not appear to address model misspecification beyond the case when outliers are present. Please revise the scope of the paper as appropriate or provide more examples to ensure outliers and model misspecification are parallel contributions rather than one nested in another.
There are many implementation details that an interested user would like to learn more but feel difficult to find from the current paper. This includes but not limited to the selection of proposal, parameter tuning, recommendations when a practitioner is being faced with a real-world problem, and computational complexity of the entire procedure. See the two referee reports for more details. The authors are also suggested to possibly provide code that is available online with recommended choices as default.
It is unclear how the proposed method outperforms existing work, either conceptually or practically. Referees have provided some competing methods for the authors to consider. I'd like to add another existing strategy in addition to the three solutions mentioned in the bottom paragraph of page 2: Bayesian fractional inference, which uses a fractional likelihood function that raises a usual likelihood function to a fractional power. What is the advantage of the proposed restrictive likelihood approach over Bayesian fractional inference, even conceptually?
Overall, the paper deserves publication after careful and thorough revision. I hope the authors can address all concerns raised in this report and the two well-grounded referee reports.

\section{Editor Comments}

Report on ìBayesian restricted likelihoods: conditioning on in su¢ cient statistics in Bayesian regressionî
The paper has received a mixed reaction from the two referees and the AE. I have a similar reaction to the paper but agree with the other readers that the content is such that an opportunity to address the issues raised is appropriate. The AEís comments place the paper on the border between Reject with Resubmission and Major Revision. I mention this because it isnít clear that a revision will be successful as there are some significant criticisms in the reviews.
My concerns might be a little different than the others and perhaps are less technical in nature. It is generally agreed that *all* models are wrong. The incorrectness of the model can arise in a number of ways and some observations being outliers is one of these. The natural question then is: how are we supposed to deal with that? The answer is surely that we don't unless the discrepancy is so substantial that the inferences would be seriously in error if we proceeded using the assumed model. This part of a statistical analysis is the model checking aspect and the solution to any issue, whatever it might be, arises there. For example, for the problem being considered in this paper, I would want a model checking procedure that indicated that there is a serious problem because, no matter what distribution was used from the model, some observations are outlying and I would want the methodology to identify the observations in question. In that case there would several ways to deal with the issue, including modifying the model, but also sim- ply discarding the o§ending observations as part of "data cleaning". It is worth noting though that the answer isn't simple because notable scientific chievements have been obtained by looking carefully at observations that are clearly discrepant.
So there are some concerns that have relevance for me and that I think the paper needs to address. What method is used to identify that there is a problem with the model such that the inferences will be strongly affected and does it identify outlying observations? A minor issue is that there may be no need to do modify the analysis but the major issue is that it introduces an arbitrariness into the analysis based on the need to chooseT: The choice of T is clearly subjective and so it needs to be subjected to the same critical analysis that we would apply to the model itself and for that matter, the prior too, and it isnít clear how to do this. I understand that there are
problems where reducing the data to some T (y) is necessary, perhaps because of computational problems associated with evaluating a likelihood, but this is clearly a compromised analysis and not one we would recommend unless forced to do so. So I don't agree with the statement made in the paper "that deliberate choice of an insufficient statistic T (y) guided by targeted inference is sound practice". There needs to be a much stronger argument for this at least for me.
The paper is well-written and thought-provoking so my hope is that a revision will be able to address the points raised.

\end{document}

### 2019-06-14 revision_2/paper.tex
revision_2 branch to work on BA revisions
first pass at addressing comments

% commands for for editing
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}{figs/}}

@@

The focus of this work is the development of techniques to handle imperfections in the likelihood $f(\by|\bth) = L(\bth|\by)$. Concern for imperfections in the likelihood are reflected in work considering minimally informative likelihoods \citep{yuan1999minimally}, sensitivities of inferences to perturbations in the model \citep{zhu2011}, the specification of a class of models and the use of Bayesian model averaging over the class \citep{clyde2004}, and considerations of such averaging when the specified class may not contain the so-called true data generating model \citep{bernardo2000, clyde2013, clarke2013Complete}.   In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study. There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling density with a mixture model which includes one component for the ``good'' data and a second component for the ``bad'' data.  With this approach, the good component of the sampling density is used for prediction of future good data.  The second approach replaces the
basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that 
often provide solid estimates of the center of the distribution but do not easily translate to predictive densities for further good data.  The third approach fits a flexible (typically nonparametric) model to  the data, producing a Bayesian version of a density estimate for both good and bad data.  In recent development, inference is made through the use of robust inference functions \citep{lee2014}.

These traditional strategies  all have their drawbacks.  The outlier-generating processes 
may be transitory in nature, constantly shifting as the source of bad data changes.  This prevents us from appealing to large-sample arguments to claim that, with enough data, we can nail down a model for both good and bad data combined.  Instead of attempting to model both good and bad data, we propose a novel strategy for handling outliers. In a nutshell, we begin with a complete model  as if all of the data are good. Rather than driving the move from prior to posterior  by the full likelihood, we use only the likelihood driven by a few summary statistics which typically target inferential quantities
of interest.  We call this likelihood a restricted likelihood because conditioning is done on a restricted set of data; the set which satisfies the observed summary statistics. This restricted likelihood leads to a formal update of the prior distribution based on the sampling density of the summary statistics. %The spirit of the approach  %The novelty of the work is twofold.  We make use of classical robust estimators as  summary statistics in a formal Bayesian framework, using the sampling density of the estimators as a replacement for the  sampling density of the data.  Second, we advance the argument that conditioning on an insufficient summary of the data is sound practice, rather than merely being done for computational and modelling convenience.

% \red{[Steve, just a reminder that a paragraph about model misspecification was here orginally but commented out by John following a referee's suggestion. I also agree with the referee in that model misspecification could be a much broader issue than having a fraction of bad data while the model for good data is correctly specified.]}
%In addition to outlier-prone data, the 
%\green{ The sampling density can err due to other forms of model misspecification.  
%The traditional view is that, if the model is inadequate, one should build a better model.  In our
%empirical work, as data sets have become larger and more complex, we have bumped into 
%settings where we cannot realistically build the perfect model.  We ask the question ``by attempting
%to improve our model through elaboration, will the overall performance of the model suffer?''  If yes,
%we avoid the elaboration, retaining a model with some level of misspecification.  Acknowledging that
%the model is misspecified implies acknowledging that the sampling density is incorrect, as
%we do when outliers are present.  Thus, outliers are but one form of misspecified model.  
%We recommend a common solution for dealing with outliers and more general forms of model misspecification.}

The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood and provides context with previous work, Section~\ref{illustrations} demonstrates some advantages of the methods on simple examples, and Section~\ref{BayesLinMod} details an MCMC algorithm to apply the method to Bayesian linear models. This computational strategy is a major contribution to the work, providing an approach to apply the method on realistic examples. Many of the the technical proofs are in the Appendix \ref{sec:appendix} with \texttt{R} code available from the authors. Sections \ref{simData} and \ref{RealData} illustrate the method with simulated data and a real insurance industry data set containing many outliers with a novel twist on model evaluation. A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method.

@@

The second example involves deliberate censoring of small and large observations. This is
sometimes done as a precursor to the analysis of reaction time experiments  \citep[e.g.,][]{ratcliff1993} where very small and large reaction times are physiologically implausible;  explained by either anticipation or lack of attention of the subject.  
With lower and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution is of mixed form, with masses $F(t_1|\bth)$ at $t_1$ and $1-F(t_2|\bth)$ at $t_2$,
and density $f(y | \bth)$ for $y \in (t_1, t_2)$.  We adjust the original data $y_i$,
producing $c(y_i)$ by defining $c(y_i)= t_1$ if $y_i \leq t_1$, $c(y_i)=t_2$ 
if $y_i \geq t_2$, and $c(y_i)=y_i$ otherwise.  
The adjusted update is performed with $L(\bth |c(\by))$.  
Letting $g(t_1|\bth) = F(t_1|\bth)$,
$g(t_2 | \bth) = 1 - F(t_2|\bth)$, and $g(y|\bth)=f(y|\bth)$ for
$y \in (t_1, t_2)$, we may rewrite the full 
likelihood as the product of two pieces
\begin{eqnarray}
\label{Censoring} 
L(\bth | \by) =  \left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i)). \right) ,  
\end{eqnarray}
Only the first part is retained in the analysis. Several more examples are detailed in \cite{lewis2014}.

@@

%\subsection{Details of Examples in Section \ref{illustrations}}
%\subsubsection{Speed of Light}
%With parameters $\beta$ and $\sigma$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with
%$\sigma^{2}$ representing measurement error. Tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.  The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$. The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models. %We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.  For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.   \citep[for details see][]{huber2009}

\section{Illustrative Examples}
\label{illustrations}
Before discussing computational details, the method is applied to two simple examples on well known data sets to demonstrate its effectiveness in situations where outliers are a major concern. The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}. %Specific details are left to the Appendix.

The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail. The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:
\begin{equation}
\beta\sim N(23.6, 2.04^{2}),\  \sigma^{2}\sim IG(5, 10), \ y_{i}\iid N (\beta, \sigma^{2}), i=1,2,\dots, n=66,
\end{equation}
where $y_{i}$ denotes the $i^{th}$ (recorded) measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with the deviations $y_i - \beta$ representing measurement error.
Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale. The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.  Two additional approaches to outlier handling are considered: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals. The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$. The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ and ensures that the prior on the variance is the same as the other models. The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ with the prior $p \sim \text{beta}(20,1)$ on the probability of belonging to the `good' component.

@@

Overall, we find that the restricted likelihood methods based on M-estimators provide the most attractive analysis for these data.  They provide sharp and appropriate inference for parameters ($\beta$) and for prediction.

%\begin{figure}[t]
%\centering
%{\includegraphics[width = 4in]{figs/speed_of_light_predictive.png}}
%\caption{dfsfsa}
%\label{fig:newcomb_predictive}
%\end{figure}
%\caption{Top: Posteriors of the location parameter $\beta$ under the normal theory model, the t-model, and four restricted likelihood models for Newcomb's speed of light measurements. Bottom: Posterior predictive distribution of the speed of light under the normal theory model, the t-model, and four restricted likelihood models.}
%\label{fig:newcomb_post}
%\end{figure}

The data and  $95\%$ credible bands for the posterior predictive distribution under each model are displayed in Figure \ref{fig:calls_predictive}. The normal model fit to all cases results in a very wide posterior predictive distribution due to an inflated estimate of the variance. The t-model provides a similar predictive distribution.  The pocket of outliers from 1963 to 1970 overwhelms the natural robustness of the model and leads to wide prediction bands.  The outliers, falling toward the end of the time period, lead to a relatively high slope for the regression.  In contrast, the normal theory model fit to only the good data results in a smaller slope and narrower prediction bands.  The predictive distribution under the restricted likelihood approach is much more precise and is close to that of the normal theory fit to the non-outlying cases. The two component mixture model provides similar results, where the predictive distribution is formulated using only the good component. For these data, the large outliers are easily identified as following a distinct regression, leaving the primary component of the mixture for non-outlying data.  In a more complex situation where the outlier generating mechanism is transient (i.e., ever changing and more complex than for these data), modeling the outliers is more difficult. As in classical robust estimation, the restricted likelihood approach avoids explicitly modeling the outliers. 
\begin{figure}[t]
\centering
{\includegraphics[width = 4in]{figs/calls_predictive.png}}
\caption{Pointwise posterior predictive intervals of log(calls) under the normal theory model fit to the non-outliers, the restricted likelihood model with Tukey's M-estimator for the slope and intercept with Huber's `proposal 2'  for scale, and a heavy-tailed t-distribution model. The first three data points were used to specify the prior with each model using the remaining 21 for fitting. The normal theory model was also fit after removing observations 14-20 (years 1963 - 1970).}
\label{fig:calls_predictive}
\end{figure}
%{\bf For the figure, add fit of normal model to all cases}

%
% and the development
%of computational strategies that allow us to truly condition on the observed $T(\by)$ and 
%fit the model in formal Bayesian fashion.  In this work, we focus
%on robustness, and natural choices of $T(\by)$ for the one-sample problem include a set of middling order statistics, a trimmed
%mean, or a classical robust estimator of location and/or scale.  
%We have previously implemented several of these methods and have found them to perform well \citep[][]{lewis2012}. Versions most extensible to the linear model include the M-estimators in the tradition of \cite{huber1964}, least median squares (LMS), and least trimmed squares (LTS). For these choices the restricted likelihood is not available in closed form, making computation of the restricted posterior a challenge. For low-dimensional statistics $T(\by)$ and parameters $\bth$, the direct computational strategies described in \cite{lewis2014} can be used to estimate the incomplete posterior conditioned on essentially any statistic.  These strategies rely on generation of complete data sets from different values of $\bth$.  
%Each complete data set leads to a statistic $T(\by)$ under $\bth$, and these generated statistics are used to estimate the density at $T(\by_{obs})$, where $\by_{obs}$ is the observed complete data. This estimate is fed into Bayes' theorem for the update from prior distribution to posterior distribution.  
%

%\subsection{A first data analysis example} %\textcolor{blue}{ADDED}
%\label{darwinAnalysis}
%Before discussing computational details of finding restricted 
%posteriors, we begin by analyzing a simple example involving
%outliers. The data consists of well known measurements of the \green{passage time} of
%light taken by Simon Newcomb in the late nineteenth century and
%contain two clear outliers on the low end. Details and data are
%available in the R package {\tt MASS} and previous analyses appear in
%\cite{stigler1977}, \cite{chan1980}, and \cite{gelman2004}. Letting
%$y_{i}$ denote the $i^{th}$ coded measurement of the passage time of light, we

>>>>

% commands for for editing
\usepackage{color}
\usepackage{ulem} % \sout
\newcommand{\red}[1]{{\color{red}#1}}
\newcommand{\blue}[1]{{\color{blue}#1}}
\newcommand{\brown}[1]{{\color{brown}#1}}
\newcommand{\green}[1]{{\color{green}#1}}
\newcommand{\magenta}[1]{{\color{magenta}#1}}
\newcommand{\response}[1]{{\color{blue}#1}}
\DeclareMathOperator*{\argmin}{\arg\!\min}
\graphicspath{{figures/}{figs/}}

@@

The focus of this work is the development of techniques to handle imperfections in the likelihood $f(\by|\bth) = L(\bth|\by)$. Concern for imperfections in the likelihood are reflected in work considering minimally informative likelihoods \citep{yuan1999minimally}, sensitivities of inferences to perturbations in the model \citep{zhu2011}, the specification of a class of models and the use of Bayesian model averaging over the class \citep{clyde2004}, and considerations of such averaging when the specified class may not contain the so-called true data generating model \citep{bernardo2000, clyde2013, clarke2013Complete}.   In practice, the imperfections in a proposed likelihood often show themselves through the presence of outliers -- cases not reflecting the phenomenon under study. \response{By this definition, outliers are spurious however, identifying them so that better inference of the phenomenon under study is of importance}. There are three main solutions to Bayesian outlier-handling.  The first is to replace the basic sampling density with a mixture model which includes one component for the ``good'' data and a second component for the ``bad'' data.  With this approach, the good component of the sampling density is used for prediction of future good data.  The second approach replaces the
basic sampling density with a thick-tailed density in an attempt to discount outliers, yielding techniques that often provide solid estimates of the center of the distribution but do not easily translate to predictive densities for further good data.  The third approach fits a flexible (typically nonparametric) model to  the data, producing a Bayesian version of a density estimate for both good and bad data.  In recent development, inference is made through the use of robust inference functions \citep{lee2014}.

These traditional strategies  all have their drawbacks.  The outlier-generating processes 
may be transitory in nature, constantly shifting as the source of bad data changes.  This prevents us from appealing to large-sample arguments to claim that, with enough data, we can nail down a model for both good and bad data combined.  Instead of attempting to model both good and bad data, we propose a novel strategy for handling outliers. In a nutshell, we begin with a complete model  as if all of the data are good. Rather than driving the move from prior to posterior  by the full likelihood, we use only the likelihood driven by a few summary statistics which typically target inferential quantities
of interest.  We call this likelihood a restricted likelihood because conditioning is done on a restricted set of data; the set which satisfies the observed summary statistics. This restricted likelihood leads to a formal update of the prior distribution based on the sampling density of the summary statistics.

\response{The advantages and disadvantages of the method are detailed throughout the paper using simulated data and real data. The main advantages we have found so far come in situations we outliers are concern and there is significant prior information for the non-outlying portion of the model that is not outweighed by the data. This is because, as with many traditional posteriors, the restricted likelihood posterior tends to the classical estimates as sample size grows. The main disadvantage over traditional robust estimate techniques are mainly computational. In Section ~\ref{BayesLinMod} we detail a data-augmented MCMC algorithm to fit the models proposed in this paper. This requires an additional computational step for each iteration of the chain. Details of the additional burden are given and one must weigh the advantages of these methods with this additional burden}

The remainder of the paper is as follows: Section~\ref{restrictedlikelihood} introduces the Bayesian restricted likelihood, provides context with previous work, and demonstrates some advantages of the methods on simple examples. Section~\ref{BayesLinMod} details an MCMC algorithm to apply the method to Bayesian linear models. This computational strategy is a major contribution to the work, providing an approach to apply the method on realistic examples. Many of the the technical proofs are in the Appendix \ref{sec:appendix} with \texttt{R} code available from the authors. Sections \ref{simData} and \ref{RealData} illustrate the method with simulated data and a real insurance industry data set containing many outliers with a novel twist on model evaluation. A discussion (Section~\ref{Conclusions}) provides some final commentary on the new method. \response{ An R package \texttt{brlm} is to implement our methods in available at \texttt{github.com/jrlewi/brlm}. Additionally all data and code for the examples in this paper are available at \texttt{https://github.com/jrlewi/brlm\char`_paper/revision\char`_2}.}

@@

The second example involves deliberate censoring of small and large observations. This is
sometimes done as a precursor to the analysis of reaction time experiments  \citep[e.g.,][]{ratcliff1993} where very small and large reaction times are physiologically implausible;  explained by either anticipation or lack of attention of the subject.  
With lower and upper censoring times at $t_1$ and $t_2$, the post-censoring sampling distribution is of mixed form, with masses $F(t_1|\bth)$ at $t_1$ and $1-F(t_2|\bth)$ at $t_2$,
and density $f(y | \bth)$ for $y \in (t_1, t_2)$.  We adjust the original data $y_i$,
producing $c(y_i)$ by defining $c(y_i)= t_1$ if $y_i \leq t_1$, $c(y_i)=t_2$ 
if $y_i \geq t_2$, and $c(y_i)=y_i$ otherwise.  
The adjusted update is performed with $L(\bth |c(\by))$.  
Letting $g(t_1|\bth) = F(t_1|\bth)$,
$g(t_2 | \bth) = 1 - F(t_2|\bth)$, and $g(y|\bth)=f(y|\bth)$ for
$y \in (t_1, t_2)$, we may rewrite the full 
likelihood as the product of two pieces
\begin{eqnarray}
\label{Censoring} 
L(\bth  | \by) =  \left( \prod_{i=1}^n g(c(y_i)  | \bth) \right) \left( \prod_{i=1}^n f(y_i|\bth,c(y_i)). \right) ,  
\end{eqnarray}

$\prod_{i=1}^n f(y_i|\bth,c(y_i))$ is the likelihood of the data conditioned on parameters and the summary statistic $c(\cdot)$ and recovers the piece of the full likelihood not in $ \prod_{i=1}^n g(c(y_i)  | \bth)$. Only the first part is retained in the analysis. Several more examples are detailed in \cite{lewis2014}.

@@

%\subsection{Details of Examples in Section \ref{illustrations}}
%\subsubsection{Speed of Light}
%With parameters $\beta$ and $\sigma$, the full model is $\beta\sim N(23.6, 2.04^{2})$, $\sigma^{2}\sim IG(5, 10)$, $y_{i}\iid N (\beta, \sigma^{2})$ for $i=1,2,\dots, n=66$ where $y_{i}$ denotes the $i^{th}$ measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with
%$\sigma^{2}$ representing measurement error. Tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality and for comparability, roughly $5\%$ of the residuals are trimmed for LTS.  The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$. The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ so the prior on the variance is the same as the other models. %We note that the variance of the data under this model is $\frac{\nu}{\nu-2}\sigma^{2}$.  For comparability, it is this quantity that has the prior distribution $IG(a,b)$ given above.   \citep[for details see][]{huber2009

\subsection{An Illustrative Example}
\label{illustrations}
Before discussing computational details, the method is applied to two simple examples on well known data sets to demonstrate its effectiveness in situations where outliers are a major concern. The first example is presented here, with the second provided in the Supplementary Material. The full model in each case fits into the Bayesian linear regression framework discussed in Section \ref{BayesLinMod}. %Specific details are left to the Appendix.

The first example is an analysis of Simon Newcomb's 66 measurements of the passage time of light \citep{stigler1977}; two of which are significant outliers in the lower tail. The full model is a standard location-scale Bayesian model also used in \cite{lee2014}:
\begin{equation}
\beta\sim N(23.6, 2.04^{2}),\  \sigma^{2}\sim IG(5, 10), \ y_{i}\iid N (\beta, \sigma^{2}), i=1,2,\dots, n=66,
\end{equation}
where $y_{i}$ denotes the $i^{th}$ (recorded) measurement of the passage time of light. $\beta$ is interpreted as the passage time of light with the deviations $y_i - \beta$ representing measurement error.
Four versions of the restricted likelihood are fit with conditioning statistics: 1) Huber's M-estimator for location with Huber's `proposal 2'  for scale 2)  Tukey's M-estimator for location with Huber's `proposal 2'  for scale 3) LMS (least median squares) for location with associated estimator of scale and 4) LTS (least trimmed squares)  for location with associated estimator of scale. \response{Details of these estimators can be found in many places, including \citep{huber2009}. We return to the two M-estimators throughout this paper as we have found them to offer good default choices for practitioners dealing with outliers. For this reason we offer a quick review of these estimators in the Supplementary Material.}  The tuning parameters for the M-estimators are chosen to achieve $95\%$ efficiency under normality \citep{huber2009} and, for comparability, roughly $5\%$ of the residuals are trimmed for LTS.  Two additional approaches to outlier handling are considered: 1) the normal distribution is replaced with a t-distribution and, 2) the normal distribution is replaced with a mixture of two normals. The t-model assumes $y_{i}\iid t_{\nu} (\beta, \sigma^{2})$ with $\nu=5$. The prior on $\sigma^{2}$ is $IG(5, \frac{\nu-2}{\nu}10)$ and ensures that the prior on the variance is the same as the other models. The mixture takes the form: $y_{i}\iid pN (\beta, \sigma^{2}) + (1-p)N(\beta, 10\sigma^{2})$ with the prior $p \sim \text{beta}(20,1)$ on the probability of belonging to the `good' component.

@@

Overall, we find that the restricted likelihood methods based on M-estimators provide the most attractive analysis for these data.  They provide sharp and appropriate inference for parameters ($\beta$) and for prediction. A second example on well known data is provided in the Supplementary Material.
